Enhancement of SDR in Thessaloniki

### 2024-01-30 GHI_enh_03_process.tex
Commit 2024-01-16 14:15
Commit 2024-01-17 12:16
Commit 2024-01-18 12:18
Commit 2024-01-19 10:14
Commit 2024-01-20 20:15
Commit 2024-01-21 00:14
Commit 2024-01-21 16:14
Commit 2024-01-30 13:15

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-01-16}

@@

Residuals:
   Min     1Q Median     3Q    Max 
-404.5 -198.5  -82.3  139.7 1090.3

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)      -7.444e+01  6.622e+01  -1.124    0.262    
as.numeric(Date)  3.317e-07  5.344e-08   6.207 1.51e-09 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 276.5 on 353 degrees of freedom
Multiple R-squared:  0.09841,   Adjusted R-squared:  0.09585 
F-statistic: 38.53 on 1 and 353 DF,  p-value: 1.513e-09
\end{verbatim}

@@

Residuals:
   Min     1Q Median     3Q    Max 
-404.5 -198.5  -82.3  139.7 1090.3

Coefficients:
                    Estimate Std. Error t value Pr(>|t|)    
(Intercept)       -7.444e+01  6.622e+01  -1.124    0.262    
ST_E_monthly$Date  3.317e-07  5.344e-08   6.207 1.51e-09 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 276.5 on 353 degrees of freedom
Multiple R-squared:  0.09841,   Adjusted R-squared:  0.09585 
F-statistic: 38.53 on 1 and 353 DF,  p-value: 1.513e-09
\end{verbatim}

@@

\begin{verbatim}
2024-01-16 09:31:56.9 athan@sagan GHI_enh_03_process.R 0.865834 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-01-30}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-414.28 -204.05  -79.81  138.47 1080.23

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)      -9.272e+01  6.658e+01  -1.393    0.165    
as.numeric(Date)  3.492e-07  5.341e-08   6.537 2.17e-10 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 282.2 on 358 degrees of freedom
Multiple R-squared:  0.1066,    Adjusted R-squared:  0.1041 
F-statistic: 42.73 on 1 and 358 DF,  p-value: 2.168e-10
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-414.28 -204.05  -79.81  138.47 1080.23

Coefficients:
                    Estimate Std. Error t value Pr(>|t|)    
(Intercept)       -9.272e+01  6.658e+01  -1.393    0.165    
ST_E_monthly$Date  3.492e-07  5.341e-08   6.537 2.17e-10 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 282.2 on 358 degrees of freedom
Multiple R-squared:  0.1066,    Adjusted R-squared:  0.1041 
F-statistic: 42.73 on 1 and 358 DF,  p-value: 2.168e-10
\end{verbatim}

@@

\begin{verbatim}
2024-01-30 10:54:28.8 athan@sagan GHI_enh_03_process.R 1.047631 mins
\end{verbatim}
